---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(pkginfo)
```
# pkginfo

> Tools for retrieving package information

[![CRAN\_Status\_Badge](https://www.r-pkg.org/badges/version/pkginfo)](https://cran.r-project.org/package=pkginfo) 
[![Travis-CI Build Status](https://travis-ci.org/rsquaredacademy/pkginfo.svg?branch=master)](https://travis-ci.org/rsquaredacademy/pkginfo) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/rsquaredacademy/pkginfo?branch=master&svg=true)](https://ci.appveyor.com/project/aravindhebbali/pkginfo) ![](https://img.shields.io/badge/lifecycle-experimental-orange.svg)

## Overview

`pkginfo` will allow users to retrieve information about a R package from [CRAN](https://cran.r-project.org/), [GitHub](https://github.com/), [Travis CI](https://travis-ci.org/), [Appveyor](https://ci.appveyor.com/), [Codecov](https://codecov.io/) & [Stack Overflow](https://stackoverflow.com/). While it was not developed keeping any specific end user in mind, package developers might find it more useful as they can monitor their R packages using a shiny app. `pkginfo` uses [cranlogs](https://cranlogs.r-pkg.org/),[crandb](https://github.com/r-hub/crandb) and [cchecksapi](https://github.com/ropenscilabs/cchecksapi) under the hood.
                                                                          ## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rsquaredacademy/pkginfo")
```

## Shiny App

Launch the shiny app with:

```{r app, eval=FALSE}
pkginfo_dashboard()
```		

## Usage

### GitHub Info

```{r gh_info}
myRepo <- GitHubRepo$new("olsrr", "rsquaredacademy")
myRepo$get_stats()
myRepo$get_issues()
myRepo$get_branches()
myRepo$get_releases()
```

### CRAN Info

```{r cran_info}
myPackage <- CranPackage$new("olsrr")
myPackage$get_version()
myPackage$get_r_dep()
myPackage$get_cran_check_results()
myPackage$get_urls()
```

### Build Status

```{r build_status}
get_status_travis("olsrr", "rsquaredacademy")
get_status_appveyor("olsrr", "rsquaredacademy")
get_code_coverage("olsrr", "rsquaredacademy")
```

### Stack Overflow Questions

```{r so}
get_so_questions("dplyr")
```

## Community Guidelines

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.
