---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(pkginfo)
```
# pkginfo

> Tools for retrieving package information

[![CRAN\_Status\_Badge](http://www.r-pkg.org/badges/version/pkginfo)](https://cran.r-project.org/package=pkginfo) 
[![Travis-CI Build Status](https://travis-ci.org/rsquaredacademy/pkginfo.svg?branch=master)](https://travis-ci.org/rsquaredacademy/pkginfo) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/rsquaredacademy/pkginfo?branch=master&svg=true)](https://ci.appveyor.com/project/rsquaredacademy/pkginfo) ![](https://img.shields.io/badge/lifecycle-experimental-orange.svg)

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rsquaredacademy/pkginfo")
```

## Usage

#### Download Statistics

```{r downloads}
get_cran_downloads("olsrr")
```

#### Travis Build Status

```{r travis}
get_status_travis("olsrr", "rsquaredacademy")
```

#### Appveyor Build Status

```{r appveyor}
get_status_appveyor("olsrr", "rsquaredacademy")
```

#### Code Coverage

```{r coverage}
get_code_coverage("olsrr", "rsquaredacademy")
```

#### GitHub Statistics

```{r github}
get_gh_stats("olsrr", "rsquaredacademy")
```

## Community Guidelines

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.
