---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(pkginfo)
```
# pkginfo

> Tools for retrieving package information.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rsquaredacademy/pkginfo")
```

## Usage

### Download Statistics

```{r downloads}
get_downloads("olsrr")
```

### CRAN Results

```{r cran_result}
check_cran_results("olsrr")
```

### Build Status

#### Travis

```{r travis}
check_travis("rsquaredacademy", "olsrr")
```

#### Appveyor

#### CRAN Results

```{r appveyor}
check_appveyor("rsquaredacademy", "olsrr")
```

### Code Coverage

```{r coverage}
check_coverage("rsquaredacademy", "olsrr")
```

### GitHub Statistics

```{r github}
get_github_info("rsquaredacademy", "olsrr")
```

## Community Guidelines

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.
